---
title: "ggrob_OriginalHomeworkCode_01"
author: "Gianna Grob"
date: "9/9/2019"
output: html_document
---

#CHALLENGE 1

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

install.packages("stringr") #Install stringr package
library(stringr)

v <- c("Stately", "plump", "Buck", "Mulligan", "came", "from", "the", "stairhead,", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed.")     
v #Create vector with seperate word strings.

x <- v[c(1,4,7,10,13,16,19,22)]
x #Creates vector with every third word extracted.

#Not sure how to use str_split to extract eveyr third word
```


#CHALLENGE 2
```{r}
m <- matrix(data=1:80,nrow=8,ncol=10,byrow=FALSE)
m #Create matrix with numbers 1 through 80 in 10 columns.

x <- m[ ,c(2,3,6)]
x #Create matrix with only columns 2, 3, and 6.

x <- m[c(6,7,8), ]
x #Create matrix with only rows 6, 7, and 8.

x <- m[c(2,3,4,5,6),c(2,3,4,5,6,7,8,9)]
x #Extract elements from row 2, column 2, all the way through row 6, column 9.
```

#CHALLENGE 3
```{r}
a <- array(400:1, dim=c(5,5,4,4))
a #Create array that is descending 400 to 1 that is 5 x 5 x 4 x 4.

a[1, 1, 1, 2] #Returns: [1] 300

a[2, 3, 2, ] #Returns: [1] 364 264 164  64

a[1:5, 1:5, 3, 3] #Returns:     
     [,1] [,2] [,3] [,4] [,5]
[1,]  150  145  140  135  130
[2,]  149  144  139  134  129
[3,]  148  143  138  133  128
[4,]  147  142  137  132  127
[5,]  146  141  136  131  126

```

#CHALLENGE 4
```{r}
#Creating list of primate taxonomy 

a <- list("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae", "Daubentoniidae")
b <- list("Lemuroidea", a)
b #To be used under Strepsirhini list
c <- list("Lorisidae", "Galagidae")
d <- list("Lorisoidea", c)
d #To be used under Strepirhini list 
e <- list("Strepsirhini", d, b)
e #To be used in final list under Primates
f <- list("Tarsiidae")
g <- list("Tarsioidea", f)
g #To be used under Haplorhini list
h <- list("Cercopithecidae", "Hylobatidae", "Hominidae")
i <- list("Catarrhini", h)
i #To be used under Anthropoidea list
j <- list("Cebidae", "Atelidae", "Pitheciidae")
k <- list("Platyrrhini", j)
k #To be used under Anthropoidea list
l <- list("Anthropoidea", k, i)
l #To be used under Haplorhini list
m <- list("Haplorhini", l, g)
m #To be used in final list under Primates
n <- list("Primates", m, e)
n

#Realize this is a very long way of doing it, is there an easier way to shorten it?
```

#CHALLENGE 5
```{r}
A = matrix(c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
A #Create 5 x 3 matrix with provided values

df <- data.frame(A) 
df #Create a data frame out of matrix "A"

df$X2 #See what is in column X2
class(df$X2) #See what class column X2 is; it is numeric 

as.logical(df$X2) #Make data in column X2 logical-valued, returns:[1] FALSE  TRUE  TRUE FALSE FALSE
df

df$X3 #See what is in column X3
class(df$X3) #See what class column X3 is; it is numeric 

as.factor(df$X3) #Make data in column X3 factor-valued, returns: 
[1] 1 2 1 1 2
Levels: 1 2

str(df$X2) 
str(df$X3)
#Both don't show the columns as logical and factor valued. Don't know why.
```

#5 Challenges Faced
1) Splitting the vector for every third element on Challenge 1.
2) Extracting the elements from row 2, column 2 to row 6, column 9 and assign them to the variable x in Challaenge 2.
3) Not knowing an easier way to make the list in Challenge 4.
4) Coercing the second column to be logical-valued and factor-valued in Challenge 5.
5) Making the logical and factor valued columns show up as such with str(). 
